The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-07-22 draft/references.tex
Incorporate Sharon's comments and update Ricker2014 in references.tex
Fix missing beta Pic b references.

@@

@@

\bibitem[Ricker et al.(2010)]{Ricker2010} Ricker, G.~R., et al.\ 2010, 
Bulletin of the American Astronomical Society, 42, \#450.06 % TESS

>>>>

\bibitem[Chauvin et al.(2012)]{Chauvin2012} Chauvin, G., et al.\ 2012, 
\aap, 542, A41 % beta Pic orbital pars

@@

\bibitem[Nielsen et al.(2014)]{Nielsen2014} Nielsen, E.~L., et al.\ 2014, 
arXiv:1403.7195 % beta Pic orbit pars

@@

\bibitem[Ricker(2014)]{Ricker2014} Ricker, G.~R.\ 2014, Journal of the 
American Association of Variable Star Observers (JAAVSO), 42, 234 % TESS
